Seasonality in governing dynamics at submesoscales

### 2016-06-15 writeup/rocha_etal.tex
Adds new ref

Our work adds to recent studies that presented modeling \cite{sasaki_etal2014}
and observational \citep{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. We suggest that the dominance at inertia-gravity waves in
Summer is a consequence of both  of submesoscale turbulence and
enhancement of inertia-gravity waves due to restratification of
the upper ocean. Of course, our study focuses on a single patch of ocean in the
vicinities of the Kuroshio Extension, which may be typical of mesoscale-rich
subtropical regions, but not
representative of other regions such as eastern boundary currents
and the middle of the subtropical gyre: care must be taken in overgeneralizing
these results.  We plan to report on the geographic variability of submesoscale
 seasonality  in a future study.

@@

\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=1.\textwidth]{figs/fig_s3.pdf}
  \caption{The seasonal variability of the WOA 2013 stratification averaged  over
  the domain and the associated gravest three pressure modes. Only the upper 450 m is shown.}
  \label{figS3}
  \end{center}
\end{figure*}

>>>>

Our work adds to recent studies that presented modeling \cite{sasaki_etal2014}
and observational \citep{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. We conjecture that the dominance at inertia-gravity waves in
Summer \citep{callies_etal2015} is a consequence of both  of submesoscale turbulence and
enhancement of inertia-gravity waves due to restratification of
the upper ocean. Of course, our study focuses on a single patch of ocean in the
vicinities of the Kuroshio Extension, which may be typical of mesoscale-rich
subtropical regions, but not
representative of other regions such as eastern boundary currents
and the middle of the subtropical gyre: care must be taken in overgeneralizing
these results.  We plan to report on the geographic variability of submesoscale
 seasonality  in a future study.

@@

\begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=1.\textwidth]{figs/fig_s3.pdf}
  \caption{The seasonal variability of the WOA 2013 stratification averaged  over
  the domain and the associated three gravest pressure modes. Only the upper 450 m is shown.}
  \label{figS3}
  \end{center}
\end{figure*}
